%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{transparent}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{0pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{0pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-4px}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\semitransp}[2][0.0]{{\transparent{#1}#2}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
  \color{gray}
  \item
  Last Updated on March 18th, 2024
\end{flushright}

\vspace{-36pt}

\begin{flushleft}
    \textbf{\Huge \scshape Lucas Rim} \\ \vspace{0pt}
    \faIcon{home} 1360 N Laurel Ave, Apt 1, West Hollywood, CA, 90046 \\
    \faIcon{phone} 816-456-4049 \\
    \small
    \faIcon{envelope}
    \href{mailto:lucasrim@gmail.com}
    {\underline{lucasrim@gmail.com}}
    \faIcon{github}
    \href{https://github.com/lucasrim}{\underline{github.com/lucasrim}} $  $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/lucasrim}{\underline{linkedin.com/in/lucasrim}} $  $
\end{flushleft}

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{JUUL Labs} $|$ \footnotesize\emph{Sr. Software Engineer}\vspace{8pt}}{April 2022 -- Feb. 2024}
      {\small{JUUL's web store is responsible for tens of millions of dollars in transactions
      annually. My team was responsible for subscriptions, excellent user experience,
      while also deploying one of the leading age verification processes in the world.}}
      \resumeItemListStart
        \resumeItem{Managed transition from Selenium to Playwright test suite to lower flakiness in
        our CI pipelines.}
        \resumeItem{Upgraded several Rails Endpoints to conform to JSON:API v1.1 standards.}
        \resumeItem{Deployed face capture technology using various vendors, tracking successful
        age estimates for account creation and store access.}
        \resumeItem{Deployed a new static support site for sunset regions for the JUUL store.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Guaranteed Rate}\vspace{8pt} $|$ \footnotesize\emph{Software Engineer}}{July 2020 -- March 2022}
      \small{Guaranteed Rate had several internal services for their loan officers to serve their
      customers, including offering a popular industry news bulletin/training platform.}
      \resumeItemListStart
        \resumeItem{Developed QA tools for loan officers to go through required process steps with
        due dates to approve or deny mortgage applications.}
        \resumeItem{Deployed training video page for Agent Advantage, a training tool for mortgage
        officers to gain insights and industry news to improve their performance.}
        \resumeItem{Led team to begin transition from our clojurescript/Re-agent frontend to a
        modern TypeScript/React.js frontend.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Clearcover} $|$ \footnotesize\emph{Software Engineer}\vspace{8pt}}{Sept. 2018 -- July 2020}
      {\small{Clearcover needed an easy to use, understandable, and elegant frontend to sell
    one of the most complicated products in the world, insurance.}}
      \resumeItemListStart
        \resumeItem{Created and maintain the auto insurance policy selection form. Each option
        would have complete scenario descriptions of when users would be covered,
        and their limits. These differed on a state by state basis.}
        \resumeItem{Created an automated testing with third-party partners using Puppeteer.js.}
        \resumeItem{Maintained image service to generate PDFs and automate emails upon policy
        binding.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Detective.io} $|$ \footnotesize\emph{Software Engineer}\vspace{8pt}}{July 2017 -- Sept. 2018}
      {\small{Detective.io was a chrome extension to help automate several processes for
      BDR/SDR teams. It would fetch data from a user's Salesforce prospect and
      automatically search for insights on who to get into contact with.}}
      \resumeItemListStart
        \resumeItem{Designed user onboarding to highlight new features and familiarize users with
        the platform.}
        \resumeItem{Maintained Chrome extension in React for automating SDR/BDR workflows and
        Salesforce integration.}
        \resumeItem{Customized browser automation workflows to meet client demands.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ReviewTrackers} $|$ \footnotesize\emph{Software Engineer}\vspace{8pt}}{April 2016 -- July 2017}
      {\small{ReviewTrackers is an online reputation management software company that allowed clients to manage
      and reply online reviews. I was tasked with migrating frontend state management systems from React's flux to
      redux, automating creation of receipts and invoices using wkhtmltopdf, and using React Native to create an iOS
      app from idea to product in five weeks.}}
      \resumeItemListStart
        \resumeItem{Transitioned front end application from flux to redux.}
        \resumeItem{Created an email campaign platform for user-generated reviews.}
        \resumeItem{Developed Android and iOS apps in React Native, shipping v1 in five weeks.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd 

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Missouri - Columbia}{2013}
      {B. Sci - Economics}{}
  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C/C++, Python, Java, JavaScript/TypeScript, HTML/CSS, \LaTeX} \\
     
     \textbf{Tools}{: Git/GitHub, Unix Shell, Webpack, VS Code, IntelliJ CLion/PyCharm/IDEA, Atom}
     
     % \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
     
    }}
 \end{itemize}

 \pagebreak
% -------------------- TRANSPARENT --------------------
 \semitransp{
  Is this transparent
 }
\end{document}